## Load library

```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(lubridate)
library(ggstatsplot)
library(ggplot2)
library(dplyr)
library(skimr)
```

## Import dataset files to R

```{r message=FALSE, warning=FALSE}
daily_activity <-read_csv("dailyActivity_merged.csv")
daily_sleep <-read_csv("sleepDay_merged.csv")
```

## Inspect loaded dataset

```{r}
head(daily_activity)
head(daily_sleep)
```
## Inspect columns of loaded dataset

```{r}
colnames(daily_activity)
colnames(daily_sleep)
```

## Convert dates to date type

```{r}
daily_activity1 <-daily_activity %>%
  mutate_at(vars(Id), as.character) %>%
  mutate_at(vars(ActivityDate), as.Date, format = "%m/%d/%y") %>%
  rename("Day"="ActivityDate") 
daily_sleep1 <-daily_sleep %>%
  mutate_at(vars(Id), as.character) %>%
  mutate_at(vars(SleepDay), as.Date, format = "%m/%d/%y") %>%
  rename("Day"="SleepDay")
head(daily_activity1)
head(daily_sleep1)
```

## Join datasets to one dataset 

```{r}
daily_data <-daily_sleep1 %>%
  right_join(daily_activity1, by=c("Id","Day")) %>%
  mutate(Weekday = weekdays(as.Date(Day, "m/%d/%Y")))
```

## Check for duplicated and null data

```{r daily_data}
daily_data <-daily_data[!duplicated(daily_data), ]
sum(is.na(daily_data))
n_distinct(daily_data$Id)
```

## Check for unique IDs

```{r}
n_unique(daily_activity$Id)
n_unique(daily_sleep$Id)
```
## Gather the summarized data

```{r}
daily_data %>%
  select(Calories,TotalMinutesAsleep, TotalDistance, TotalSteps, VeryActiveMinutes, FairlyActiveMinutes, SedentaryMinutes) %>%
  summary()
```

## Display Bar Chart for Average steps per Day

```{r}
average_steps <- daily_data %>%
  group_by(Weekday) %>%
  summarize(Average_steps = mean(TotalSteps, na.rm = TRUE))
ggplot(average_steps, aes(x = reorder(Weekday, Average_steps), y = Average_steps)) +
  geom_bar(stat = "identity", fill = "darkgreen") +
  labs(x = "Weekdays", y = "Average Steps", title="Average steps per Day") 
```


## Display Plot with correlation for Calories burned per Very Active Minutes

```{r}
ggscatterstats(
  data = daily_data,
  x=VeryActiveMinutes,
  y=Calories,
  type="parametric"
) + labs(title="Very Active Minutes vs Calories")
```

## Display Plot with correlation for Calories burned per Fairly Active Minutes 
```{r}
ggscatterstats(
  data = daily_data,
  x=FairlyActiveMinutes,
  y=Calories,
  type="parametric"
) + labs(title="Fairly Active Minutes vs Calories")
```
## Display Plot with correlation for Calories burned versus Total Minutes Asleep

```{r}
ggscatterstats(
  data = daily_data,
  x=Calories ,
  y=TotalMinutesAsleep    ,
  type="parametric"
) + labs(title="Calories vs TotalMinutesAsleep")
```

## Display Plot with correlation for Sedentary Minutes versus Total Minutes Asleep

```{r}
ggscatterstats(
  data = daily_data,
  x=SedentaryMinutes,
  y=TotalMinutesAsleep    ,
  type="parametric"
) + labs(title="SedentaryMinutes vs TotalMinutesAsleep")
```



